Writing Trash Bin

### 2024-08-22 writingdumpster.qmd
edit evaluation bit

>>>>

# Alternative maps

```{r}
#| echo: false
#| message: false
#| warning: false
#| eval: false
#| label: fig-bivariate2
#| layout-ncol: 3
#| layout-valign: "bottom"

#fig-cap: "A bivariate map that depict the counties of Iowa where each county is coloured acording to it's average daily temperature and the variance in temperature. This map is a variation on the previous bivariate map where instead of variance being mapped to colour saturation, it is mapped to colour value. Even though colour value is intergrable with colour hue, and colour value is naturally accociated with uncertainty, the spatial trend is still visible in the map."

# Bivariate Map
# Make bivariate palette
# Function to devalue by a certain amount
colsupress2 <- function(basecols, hue=1, sat=1, val=1) {
    X <- diag(c(hue, sat, val)) %*% rgb2hsv(col2rgb(basecols))
    hsv(pmin(X[1,], 1), pmin(X[2,], 1), pmin(X[3,], 1))
}

# recurvisely decrease value
v_val = 1.1
bivariatepal2 <- c(basecols,
                   colsupress2(basecols, val=v_val), 
                   colsupress2(colsupress2(basecols, val=v_val), val=v_val),
                   colsupress2(colsupress2(colsupress2(basecols, val=v_val), val=v_val), val=v_val)
                   )

# establish levels of palette
names(bivariatepal2) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")

# Bivariate maps 2
p2a1 <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = bivariatepal2) +
  theme_void() + 
  theme(legend.position = "none")

p2b2 <- p2a1 %+% filter(my_map_data, variance_class=="highvar")

p2a1
p2b2
#show_pal2(colours = bivariatepal2, ncol=8, borders=NA, myxlab = "Temperature", myylab = "Variance", breaks = 21:29, breaks2 = 0:4)

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-transparency
#| fig-cap: "A bivariate map that depict the counties of Iowa where each county is coloured acording to it's average daily temperature and variance. This map is a variation on the previous bivariate map where instead of variance being mapped to colour saturation, it is mapped to transparency."
#| fig-subcap: 
#|   - "Low Variance Data"
#|   - "High Variance Data"
#|   - "Transparency Palette"
#| layout-ncol: 3
#| layout-valign: "bottom"

# ALTERNATIVE TRANSPARENCY INSTEAD OF COLOUR VALUE
# get colour values from transparency transformation
transpal <- lapply(basecols, scales::alpha, alpha=c(0.95, 0.65, 0.35, 0.05))

transpal <- as.vector(matrix(unlist(transpal), ncol = 4, byrow = TRUE))

names(transpal) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")

# Transparency maps
pta <- my_map_data |>
  filter(variance_class=="lowvar") %>%
  ggplot() +
  geom_sf(aes(fill = biclass, geometry = geometry), colour=NA) + 
  scale_fill_manual(values = transpal) +
  theme_void() + 
  theme(legend.position = "none")

ptb <- pta %+% filter(my_map_data, variance_class=="highvar")

pta
ptb
show_pal2(colours = transpal, ncol=8, borders=NA, myxlab = "Temperature", myylab = "Variance", breaks = 21:29, breaks2 = 0:4)
